\documentclass[11pt,twoside,openright]{report}
\usepackage[a4paper,width=155mm, inner=25mm, top=30mm,bottom=40mm, marginparsep=0mm]{geometry}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc} 
\usepackage{longtable}
\usepackage[czech]{babel} 
\usepackage{graphicx}
\usepackage{emptypage} % maže číslování na prázdných stranách
\usepackage[numbers,sort&compress]{natbib}
\usepackage{formatting,amsfonts,amsmath,amssymb}
\usepackage{booktabs,mathtools}
\usepackage{lipsum,url}
\usepackage[unicode]{hyperref}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{array}
\usepackage{float}
\usepackage{mwe}
\usepackage{appendix}
\usepackage{pdfpages}
\usepackage{etoolbox}
\usepackage[nottoc]{tocbibind}
\usepackage{tikz}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{csquotes}
\usetikzlibrary{shapes, arrows.meta}
\usetikzlibrary{backgrounds,calc}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\BeforeBeginEnvironment{appendices}{\gdef\thechapter{\ }}
\AtBeginEnvironment{appendices}{\renewcommand\thesection{\Alph{section}}}

% \cmidrule have problem with Czech
\usepackage{regexpatch}
\makeatletter
% Change the `-` delimiter to an active character
\xpatchparametertext\@@@cmidrule{-}{\cA-}{}{}
\xpatchparametertext\@cline{-}{\cA-}{}{}
\makeatother

%\usepackage[nottoc,numbib]{tocbibind}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{fancybox}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\makeatletter
\renewcommand{\ALG@name}{Algoritmus}
\makeatother
\pagestyle{fancy}
%\renewcommand{\chaptermark}[1]{%
%  \markboth{\MakeUppercase{\thechapter\ \quad  #1}}{}% 
%}
\renewcommand{\chaptermark}[1]{%
  \markboth{\MakeUppercase{#1}}{}% 
}
\fancyfoot{}{}{}
\fancyhead[LO,LE]{}
\fancyhead[RO]{\leftmark}
\fancyhead[RE]{}
\fancyfoot[RO]{\vspace*{0.8\baselineskip}\thepage}
\fancyfoot[LE]{\vspace*{0.8\baselineskip}\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\fancypagestyle{plain}{%
\fancyhead[RO]{}
\fancyhead[LO,LE]{}
\fancyfoot[RO]{\vspace*{0.8\baselineskip}\thepage}
\fancyfoot[LE]{\vspace*{0.8\baselineskip}\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
}
\makeatletter
\renewcommand\@dotsep{300}   % default value 4.5
\makeatother

\linespread{1.25}
\let\cleardoublepage=\clearpage
\begin{document}
\pagenumbering{gobble}

\input{VNITRNOSTI/main_info}
% TAK AT TO JDE OD RUKY

\input{VNITRNOSTI/uvod}

\input{VNITRNOSTI/ese}
\input{VNITRNOSTI/vysledky}
\input{VNITRNOSTI/zaver}

\renewcommand{\bibname}{Publikace autora}
\begin{thebibliography}{A}
\end{thebibliography}

\begin{enumerate}[label={[V\arabic*]}]
    \item \label{ese_mdpi} VRBA, Jan; MAREŠ, Jan. Introduction to Extreme Seeking Entropy. \textit{Entropy}, 2020, 22.1: 93.
  	\item \label{appel2}VRBA, Jan; MAREŠ, Jan. Computational Performance of the Parameters Estimation in Extreme Seeking Entropy Algorithm. In: \textit{2020 International Conference on Applied Electronics (AE)}. IEEE, 2020. p. 1-4.
	\item \label{appel3}VRBA, Jan; MAREŠ, Jan. ROC Analysis of Extreme Seeking Entropy for Trend Change Detection. In: \textit{2020 International Conference on Applied Electronics (AE)}. IEEE, 2020. p. 1-4.  
	\item \label{artep}VRBA, Jan. Využití fuzzy systémů a algoritmu learning entropy pro detekci změn stavů bioprocesu. In: \textit{Automatizacia a riadenie v teorii a praxi ARTEP 2017}. Technická univerzita Košice, 2017.

	\item \label{asr} VRBA, Jan. \textit{XLIII. Seminář ASŘ - Adaptivní metoda detekce} [přednáška]. Ostrava: VŠB TU Ostrava, 27.4.2018.
    \item \label{appel1}VRBA, Jan. Adaptive Novelty Detection with Generalized Extreme Value Distribution. In: \textit{2018 International Conference on Applied Electronics (AE)}. IEEE, 2018. p. 1-4.
    \item \label{ijcnn}BUKOVSKÝ, Ivo, et al. Study of learning entropy for onset detection of epileptic seizures in EEG time series. In: \textit{2016 International Joint Conference on Neural Networks (IJCNN)}. IEEE, 2016. p. 3302-3305.

    
    \item \label{cyril}OSWALD, Cyril, et al. Novelty Detection in System Monitoring and Control with HONU. In: \textit{Applied Artificial Higher Order Neural Networks for Control and Recognition}. IGI Global, 2016. p. 61-78.


	\item \label{roboti}VRBA, Jan, et al. An Automated Platform for Microrobot Manipulation. In: \textit{International Workshop on Soft Computing Models in Industrial and Environmental Applications}. Springer, Cham, 2020. p. 255-265.
	\item \label{bila1}BÍLA, Jiří; VRBA, Jan. The Detection and Interpretation of Emergent Situations in ECG Signals. In: \textit{International Conference on Soft Computing-MENDEL}. Springer, Cham, 2016. p. 264-275.

	\item \label{ijcnn3}MOJZES, Matej, et al. Feature selection via competitive levy flights. In: \textit{2016 International Joint Conference on Neural Networks (IJCNN)}. IEEE, 2016. p. 3731-3736.
	
	\item \label{bila2}BÍLA, Jiří; NOVÁK, Martin; VRBA, Jan. Detection of emergent situations in complex systems represented by algebras of transformations. In: \textit{MATEC Web of Conferences}. EDP Sciences, 2016. p. 02035.	
	\item \label{artep2}BUKOVSKÝ, Ivo, OSWALD, Cyril, VRBA, Jan. Případová studie použití entropie učení pro adaptivní detekci při řízení spalování tuhých paliv. In: \textit{Automatizácia a riadenie v teórii a praxi 2015}. Technická univerzita Košice, 2015.
\end{enumerate}

\renewcommand{\bibname}{Literatura relevantní k tezím}
\begin{thebibliography}{L}
\bibitem{expo}SHARMA, Anish and ANDREWS, Rebecca. Managing-Exponential-Data-Growth-and-Application-Modernization. \textit{IBM} [online]. 11 November 1999. [cit. 11.8.2020]. Dostupné z: https://www.ibm.com/cloud/blog/managing-exponential-data-growth-and-application-modernization 
\bibitem{ivoLE1}BUKOVSKY, Ivo. Learning entropy: Multiscale measure for incremental learning. \textit{Entropy}, 2013, 15.10: 4159-4187.
\bibitem{ivoLE2}BUKOVSKY, Ivo; KINSNER, Witold; HOMMA, Noriyasu. Learning Entropy as a Learning-Based Information Concept. \textit{Entropy}, 2019, 21.2: 166.
\bibitem{elbnd1}CEJNEK, Matous; BUKOVSKY, Ivo. Concept drift robust adaptive novelty detection for data streams. \textit{Neurocomputing}, 2018, 309: 46-53.
\bibitem{elbnd2} CEJNEK, Matous; BUKOVSKY, Ivo. Influence of type and level of noise on the performance of an adaptive novelty detector. In: \textit{2017 IEEE 16th International Conference on Cognitive Informatics \& Cognitive Computing (ICCI* CC)}. IEEE, 2017. p. 373-377.
\bibitem{elbnd3}CEJNEK, Matous; BUKOVSKY, Ivo; VYSATA, Oldrich. Adaptive classification of EEG for dementia diagnosis. In: \textit{2015 International Workshop on Computational Intelligence for Multimedia Understanding (IWCIM)}. IEEE, 2015. p. 1-5.
\bibitem{mackey}MACKEY, Michael C.; GLASS, Leon. Oscillation and chaos in physiological control systems. \textit{Science}, 1977, 197.4300: 287-289.
\bibitem{dead}SPANGENBERG, Mariana, et al. Detection of variance changes and mean value jumps in measurement noise for multipath mitigation in urban navigation. \textit{Navigation}, 2010, 57.1: 35-52.
\bibitem{stepchange}L'ECUYER, Pierre. History of uniform random number generation. In: \textit{2017 Winter Simulation Conference (WSC)}. IEEE, 2017. p. 202-230.
\bibitem{diagnosis}MAURYA, Mano Ram; RENGASWAMY, Raghunathan; VENKATASUBRAMANIAN, Venkat. Fault diagnosis using dynamic trend analysis: A review and recent developments. \textit{Engineering Applications of artificial intelligence}, 2007, 20.2: 133-146.
\bibitem{roc_orig}EGAN, James P. \textit{Signal detection theory and ROC-analysis}. Academic press, 1975.
\bibitem{roc_bible}FAWCETT, Tom. An introduction to ROC analysis. \textit{Pattern recognition letters}, 2006, 27.8: 861-874.
\bibitem{fault}GERTLER, Janos. \textit{Fault detection and diagnosis in engineering systems}. CRC press, 1998.
\bibitem{data_streams}YU, Kangqing, et al. Real-time Outlier Detection over Streaming Data. In: \textit{2019 IEEE SmartWorld, Ubiquitous Intelligence \& Computing, Advanced \& Trusted Computing, Scalable Computing \& Communications, Cloud \& Big Data Computing, Internet of People and Smart City Innovation (SmartWorld/SCALCOM/UIC/ATC/CBDCom/IOP/SCI)}. IEEE, 2019. p. 125-132.
\bibitem{surveilance}
RAMEZANI, Ramin; ANGELOV, Plamen; ZHOU, Xiaowei. A fast approach to novelty detection in video streams using recursive density estimation. In: \textit{2008 4th International IEEE Conference Intelligent Systems. IEEE, 2008}. p. 14-2-14-7.
\bibitem{robotics_marslan}
MARSLAND, Stephen; NEHMZOW, Ulrich; SHAPIRO, Jonathan. On-line novelty detection for autonomous mobile robots. \textit{Robotics and Autonomous Systems}, 2005, 51.2-3: 191-206.
\bibitem{robotics}
NEHMZOW, Ulrich, et al. Novelty detection as an intrinsic motivation for cumulative learning robots. In: \textit{Intrinsically Motivated Learning in Natural and Artificial Systems}. Springer, Berlin, Heidelberg, 2013. p. 185-207.
\bibitem{python}VAN ROSUM, G.; DRAKE, F. L. \textit{Python 3 Reference Manual}. Scotts Valley, CA: CreateSpace, 2009.
\bibitem{numpy}OLIPHANT, Travis E. \textit{A guide to NumPy (Vol. 1)}. Trelgol Publishing USA, 2006.
\bibitem{scipy}VIRTANEN, P. et al.  SciPy 1.0: Fundamental Algorithms for Scientific Computing in Python. \textit{Nature Methods}, 2020, 17(3), 261-272.
\end{thebibliography}
\cleardoublepage
\thispagestyle{empty}\

\newpage
\end{document}